\normalsize
\begin{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Define the longtable
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{longtable}{cccccc >{\scriptsize}p{3cm}}
%\begin{longtable}{>{\scriptsize}p{3cm} >{\scriptsize}p{6cm} >{\scriptsize}p{4cm} >{\scriptsize}p{3cm} >{\scriptsize}p{3cm} >{\scriptsize}p{3cm} >{\scriptsize}p{3cm} >{\scriptsize}p{3cm} >{\scriptsize}p{3cm} >{\scriptsize}p{3cm}}
\begin{longtable}{c >{\scriptsize}p{8cm} c}

\multicolumn{3}{c}{\normalsize \bf 50-pin header connections to signal generation board (J1401)}\\
\hline

\bf Net name	
&\bf \normalsize \centering Description
&\bf J1401:pin	
\endfirsthead	%now we're done defining the firt table heading


\multicolumn{3}{c}{\small \sl Continued from previous page}\\
\hline

\bf Net name	
&\bf \normalsize \centering Description
&\bf J1401:pin
\endhead	%now we're done defining the table heading on everything but the first page

\\ \hline
\multicolumn{3}{c}{\small \sl Continued on next page}\\
\endfoot%now we're done defining the foot of tables right before a page break
\hline
\caption{\normalsize 50-pin header connections to signal generation board (J1401)}
\endlastfoot%now we're done defining the last foot of the table
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Start the table data 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Net name		%Description		%Connector and pin

\verb80V_dig8
&Ground reference from the signal generation board
&1\\

\verb8ser_clk_int8
&Clock for internal serial devices.  The devices shift data on the clock edges, making this an edge-sensitive line that should be filtered.
&2\\

\verb8ser_data_int8
&Data for internal serial devices.  Data is level-sensitive and doesn't need filtering.
&3\\

\verb80V_dig8
&Ground reference from the signal generation board
&4\\

\verb8bwidth_ctrl_sr_cs8
&Bandwidth control shift register chip select.  I call this a chip select, but it's really an edge-sensitive storage register clock.  So it needs to be filtered.
&5\\

\verb8analog_oe_n8
&\begin{minipage}[t]{8cm}
	\raggedright
	Output enable for all analog shift registers, both inside the box and in the buddy box:
	\begin{tabular}{cl}
	\textbf{1}	&\parbox[t]{7cm}{Shift registers disabled -- registers have high Z outputs but will accept data}\\	
	\textbf{0}	&Shift registers enabled\\
	\end{tabular}	
\end{minipage}
&6\\



\verb8off_dac_a_cs8
&Chip select for first quad 12-bit DAC. Level sensitive. 
&7\\

\verb8off_dac_b_cs8
&Chip select for second quad 12-bit DAC. Level sensitive. 
&8\\

\verb8extin_gain_cs8
&Chip select for external input gain calibration multiplying DAC.  Level sensitive.  
&9\\

\verb8limiting8
&Output from the voltage clamp comparator
&10\\

\verb8fp_igain_cs8
&Front panel I/V gain trim multiplying DAC chip select. Level sensitive.
&11\\

\verb8int_iv_sr_cs8
&Chip select for the internal I/V shift register.  I call this a chip select, but it's really an edge-sensitive storage register clock.  So it needs to be filtered.
&12\\

\verb80V_dig8
&Ground reference from the signal generation board
&13\\

\verb8int_vm_sr_cs8
&Chip select for the internal voltmeter shift register.  I call this a chip select, but it's really an edge-sensitive storage register clock.  So it needs to be filtered.
&14\\

(spare)
&Connected to test point
&15\\

\verb80V_dig8
&Ground reference from the signal generation board
&16\\

\verb80V_dig8
&Ground reference from the signal generation board
&17\\

\verb8e_adc_data8
&E ADC dedicated data line
&18\\

\verb8adc_clk8
&Clock for the ADCs.  Edge sensitive -- needs filtering.
&19\\

\verb80V_dig8
&Ground reference from the signal generation board
&20\\

\verb8i_adc_data8
&I ADC dedicated data line
&21\\

\verb8adc_convert8
&Conversion signal for the E, I, and sync ADCs.  Edge sensitive -- needs filtering.
&22\\

\verb80V_dig8
&Ground reference from the signal generation board
&23\\

\verb8sync_adc_data8
&sync ADC dedicated data line
&24\\

\verb80V_dig8
&Ground reference from the signal generation board
&25\\

\verb8fp_egain_cs8
&Chip select for the front panel E out gain trim multiplying DAC.  Level sensitive.
&26\\

\verb8ebias_cs8
&Chip select for the E bias rejection DAC.  Level sensitive.
&27\\

\verb8rp_egain_cs8
&Chip select for the rear panel E out gain trim multiplying DAC. Level sensitive.
&28\\

\verb8boost_dac_cs8
&Chip select for the current interrupt boost DAC. Level sensitive.
&29\\

\verb8pos_fbck_cs8
&Chip select for the positive feedback multiplying DAC. Level sensitive.
&30\\

\verb8rp_igain_cs8
&Chip select for rear panel I out gain trim multiplying DAC. Level sensitive.
&31\\

\verb8interrupt8
&\begin{minipage}[t]{5cm}
	\raggedright
	Controls the AC switch:
	\begin{tabular}{cl}
	\textbf{1}	&AC switch closed\\	
	\textbf{0}	&AC switch open\\
	\textbf{Z}	&AC switch open\\
	\end{tabular}	
\end{minipage}
&32\\

\verb8cemon_gain_cs8
&Chip select for the CE monitor gain trim multiplying DAC. Level sensitive.
&33\\

\verb8sw_sense8
&\begin{minipage}[t]{5cm}
	\raggedright
	Indicates the status of the AC switch:
	\begin{tabular}{cl}
	\textbf{1}	&Front panel switch ``in'' (closed) and AC switch closed\\
	\textbf{0}	&AC switch open\\	
	\end{tabular}	
\end{minipage}
&34\\

\verb80V_dig8
&Ground reference from the signal generation board
&35\\

\verb8ser_data_out_ext8
&Serial data to be sent to the buddy box. Level sensitive.
&36\\

\verb8ee_cs_ext8
&Chip select for the eeprom in the buddy box.  Level sensitive.
&37\\

\verb8ser_clk_ext8
&Clock for serial devices in the buddy box.  Edge sensitive -- needs filtering.
&38\\

\verb8sr_cs_ext8
&Chip select for the shift register in the buddy box.  Level sensitive.
&39\\

(spare)
&Connected to test point
&40\\

\verb8ser_data_in_ext_buff8
&Serial data from the buddy box eeprom.  Level sensitive.
&41\\

\verb80V_dig8
&Ground reference from the signal generation board
&42\\

\verb80V_dig8
&Ground reference from the signal generation board
&43\\

\verb8surge8
&\begin{minipage}[t]{7cm}
	\raggedright
	Maximum current flag from the power amplifier
	\begin{tabular}{cl}
	\textbf{1}	&Power amplifier output current $>1.2$A\\
	\textbf{0}	&OK\\
	\end{tabular}	
\end{minipage}
&44\\

\verb8+20V_sig8
&+20V analog rail
&45\\

\verb8-20V_sig8
&-20V analog rail
&46\\

\verb8tsense8
&\begin{minipage}[t]{5cm}
	\raggedright
	Thermal flag from the power amplifier
	\begin{tabular}{cl}
	\textbf{1}	&Power amplifier die temperature $>140\celsius$\\
	\textbf{0}	&OK\\
	\end{tabular}	
\end{minipage}
&47\\

\verb80V_dig8
&Ground reference from the signal generation board
&48\\

\verb8+20V_sig8
&+20V analog rail
&49\\

\verb8-20V_sig8
&-20V analog rail
&50\\


\end{longtable}
\end{center}
\normalsize
